\pdfminorversion=4
\documentclass[a4paper,10pt]{article}

%%%%%%%%%%%%%%%%%%%
% Packages/Macros %
%%%%%%%%%%%%%%%%%%%
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern} % Clean, modern font
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}

%%%%%%%%%%%
% Margins %
%%%%%%%%%%%
\geometry{margin=0.6in}

%%%%%%%%%%%%%%%%%%%%%%%%
% Section Styling %
%%%%%%%%%%%%%%%%%%%%%%%%
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{6pt}{4pt}
\setlist[itemize]{leftmargin=*, itemsep=0pt, topsep=0pt, parsep=0pt}

%%%%%%%%%%%%%%%%%%%%
% Hyperlink Style  %
%%%%%%%%%%%%%%%%%%%%
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=black,
    citecolor=black
}

%%%%%%%%%%%%%%%%
% Document %
%%%%%%%%%%%%%%%%
\begin{document}
\pagestyle{empty}

%%%%%%%%%%%%%%%%
% Header %
%%%%%%%%%%%%%%%%
\begin{center}
    {\huge\bfseries Rajon Dey} \\
    \vspace{2mm}
    {\large Software Engineer | Frontend Lead | Full-Stack Developer} \\
    \vspace{3mm}
    \href{mailto:rajon.dey.dev@gmail.com}{rajon.dey.dev@gmail.com} \quad|\quad
    +8801737997143 \quad|\quad
    \href{https://portfolio.rajondey.com}{portfolio.rajondey.com} \\
    \href{https://linkedin.com/in/rajondey}{linkedin.com/in/rajondey} \quad|\quad
    \href{https://github.com/RajonDey}{github.com/RajonDey}
\end{center}

\vspace{3mm}
\hrule
\vspace{3mm}

%%%%%%%%%%%%%%%%%%%%%%%%%
% Professional Summary %
%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Professional Summary}
Software Engineer with 9+ years of experience across frontend and full-stack development. Currently serving as a \textbf{Module Lead – Frontend} at SJ Innovation, where I lead a team of 8+ developers and deliver scalable React/Next.js and MERN applications. Skilled in turning complex requirements into maintainable systems, improving performance (30\% faster load times, 40\% higher Lighthouse scores), and mentoring juniors to strengthen team productivity. Beyond client projects, I actively build products like \textbf{ClipKit (SaaS platform)} and contribute to research in AI security. Passionate about crafting web applications that balance speed, scalability, and clean architecture.

%%%%%%%%%%%%%%%%
% Skills %
%%%%%%%%%%%%%%%%
\section*{Technical Skills}
\begin{itemize}[leftmargin=*,itemsep=0.5pt]
    \item \textbf{Frontend:} React, Next.js, TypeScript, SCSS, Tailwind CSS
    \item \textbf{Backend:} Node.js, Express, FastAPI, Python, PHP
    \item \textbf{Databases:} PostgreSQL, MongoDB, MySQL, Redis
    \item \textbf{DevOps:} AWS (EC2, S3, Lambda), Docker, GitHub Actions, CI/CD
    \item \textbf{Other:} WordPress, Headless CMS, Blockchain Integration
    \item \textbf{Leadership:} Mentoring, code reviews, agile workflows, project planning
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%
% Professional Experience %
%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Professional Experience}

\textbf{Module Lead – Frontend} \hfill May 2019 – Present \\
SJ Innovation LLC
\begin{itemize}[leftmargin=*,itemsep=0.5pt]
    \item Lead a team of 8+ developers, delivering 100+ websites and SaaS platforms serving 100K+ monthly users.
    \item Architected and deployed 15+ MERN-stack applications handling 5K+ daily active users.
    \item Improved React/Next.js app performance, reducing load times by 30\% and boosting Lighthouse scores by 40\%.
    \item Introduced CI/CD pipelines that cut deployment time by 60\%.
    \item Mentored junior engineers, improving code quality and team productivity by 25\%.
\end{itemize}
\textit{Key Achievements:} Employee of the Month (Nov 2020); Performer of the Month (10+ times since 2019)

\textbf{Freelance Web Developer} \hfill Jan 2015 – Dec 2019
\begin{itemize}[leftmargin=*,itemsep=0.5pt]
    \item Completed 200+ client projects (e-commerce, blogs, SaaS apps) with consistent 5-star ratings.
\end{itemize}

%%%%%%%%%%%%%%%%
% Projects %
%%%%%%%%%%%%%%%%
\section*{Projects}
\begin{itemize}[leftmargin=*,itemsep=0.5pt]
    \item \textbf{ClipKit (SaaS Platform):} Full-stack content creation tool built with FastAPI, PostgreSQL, and AI integration. \href{https://github.com/RajonDey/clipkit-app}{[GitHub]}
    \item \textbf{Online IELTS Test Platform:} A full-fledged platform for IELTS test preparation and practice. \href{https://ielts-test-platform-0-01.vercel.app/}{[Live]}
    \item \textbf{LLM Security Research:} Research on AI model vulnerabilities, published findings on jailbreak methods. \href{https://llm-vulnerability-site.vercel.app/}{[Live]}
\end{itemize}

%%%%%%%%%%%%%%%%
% Education %
%%%%%%%%%%%%%%%%
\section*{Education}
\textbf{BBA (Finance \& Banking)} \hfill Jan 2013 – Nov 2017 \\
Leading University, Sylhet, Bangladesh

%%%%%%%%%%%%%%%%
% Certifications %
%%%%%%%%%%%%%%%%
\section*{Certifications}
\begin{itemize}[leftmargin=*,itemsep=0.5pt]
    \item AWS Educate (5 Badges) – 2024
    \item Google AI for Anyone (EdX) – 2024  
    \item Advanced Python Programming – 2025
    \item Mastering React (Code With Mosh) – 2022
\end{itemize}

%%%%%%%%%%%%%%%%
% Footer %
%%%%%%%%%%%%%%%%
\begin{center}
    \vspace{3mm}
    \small Last updated: \today
\end{center}

\end{document}
